\textmd{\hmwkClass:\ \hmwkTitle}\\ \normalsize{\hmwkClassInstructor}\\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-08 paper/main.tex
Added to physics engine

\section{Physics Engine}
There are mainly two ways we could update object positions: 1) The evolver can take in a list of forces and objects and apply forces as appropriate 2) Each object can be registered with a set of forces applicable to them and the evolver can call each object to evolve themselves.

There are three types of objects in the system: $thing$, $interaction$, and $world$. $thing$ refers to all physical objects in the system. There is a hierarchy of physical objects that have additional properties. For example, type $magnet$ has an additional property $charge$ and experiences magnetic forces while type $ball$ experiences only gravity. Each $thing$ keeps a list of $interactions$ that is used to update itself. $interaction$ refers to forces exerted on $thing$. $interaction$ includes a procedure that calculates the force as well as $influence$, a list of $thing$ that contribute to that force. Similar to $thing$, subtypes of $interaction$  form a hierarchy. Lastly, $world$ keeps a list of all $things$ and an $update$ call to the $world$ calls on each $thing$ to update itself.

@@

Our engine updates each object every timestep and re-renders them on the screen:
\begin{verbatim}
(define (run-engine world steps)
  (reset-graphics)
  (if (> steps 0)
    (begin 
      (for-each 
        (lambda (thing)
            (newline)
            (display (cons (get-name thing) (get-position thing)))  ; for debugging
            (render thing))
        (get-world-all-things world))
      (update-world world)
    (run-engine world (- steps 1)))))
\end{verbatim}

>>>>

\section{Physics Engine}
\subsection{Object Types}
There are three types of objects in the system: \texttt{thing}, \texttt{interaction}, and \texttt{world}. \texttt{thing} refers to all physical objects in the system. There is a hierarchy of physical objects that have additional properties. For example, type \texttt{magnet} has an additional property \texttt{charge} and experiences magnetic forces while type \texttt{ball} experiences only gravity. Each \texttt{thing} keeps a list of \texttt{interaction} that is used to update itself. \texttt{interaction} refers to forces exerted on \texttt{thing}s. \texttt{interaction} includes a procedure that calculates the force as well as \texttt{influences}, a list of \texttt{thing}s that contribute to that force. Similar to \texttt{thing}, subtypes of \texttt{interaction}s form a hierarchy. Lastly, \texttt{world} keeps a list of all \texttt{thing}s and an \texttt{update} call to the \texttt{world} calls on each \texttt{thing} to update itself.

@@

\subsection{Updating Physical Objects}
There are mainly two ways we could update object positions: 1) The evolver can take in a list of forces and objects and apply forces as appropriate 2) Each object can be registered with a set of forces applicable to them and the evolver can call each object to evolve themselves.

\subsection{Output Display}
Our engine updates each object every timestep and re-renders them on the screen:
\begin{verbatim}
(define (run-engine world steps)
  (reset-graphics)
  (if (> steps 0)
    (begin 
      (for-each 
        (lambda (thing)
            (newline)
            (display (cons (get-name thing) (get-position thing)))  ; for debugging
            (render thing))
        (get-world-all-things world))
      (update-world world)
    (run-engine world (- steps 1)))))
\end{verbatim}
